---
title: "2019 Data Course"
author: "Mirko Maelicke"
date: "20 1 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(RPostgreSQL)
library(knitr)
library(dplyr)
library(ggplot2)

# load my functions
source('lib.R')

# create connection to DB with cmd args
drv = dbDriver('PostgreSQL')
con <- dbConnect(drv, host='v45522.1blu.de', port=5432, 
                 user=commandArgs(trailingOnly = T)[1], password= commandArgs(trailingOnly = T)[2],
                 dbname='datamanagement')
```

## 2019 Data overview

### distribution

This short 'analysis' script shall demonstrate how we can use Github to create automated reports on the collected data in a collaborative way.
The following table summarizes all sensor locations used in 2019:

```{sql connection=con, output.var='hobos.2019'}
select hobo_id, radiation_influence, longitude, latitude,
  avg(min_t) as min_t, avg(max_t) as max_t, avg(mean_t) as mean_t, avg(p90_t) as p90_t
from
(
  select
    h.hobo_id, h.radiation_influence, st_x(h.geom) as longitude, st_y(h.geom) as latitude,
    date_trunc('hour', d.tstamp) as hour,
    max(d.temperature) as max_t,
    min(d.temperature) as min_t,
    avg(d.temperature) as mean_t,
    percentile_cont(0.9) within group (order by d.temperature) as p90_t
  from hobo h
  join raw_data d on d.hobo_id=h.hobo_id
  where h.year=2019 and d.tstamp > '2018-12-24' and d.tstamp < '2019-01-07'
  and st_y(h.geom) < 48.1 and st_x(h.geom) > 7.8
  and d.light > 250 and d.light < 2500
  group by h.hobo_id, h.radiation_influence, st_x(h.geom), st_y(h.geom), date_trunc('hour', d.tstamp)
) as hour
group by hobo_id, radiation_influence, longitude, latitude
```
```{r}
kable(hobos.2019, caption='All of 2019\'s HOBO locations')
```

The database is searched on compile time of this RMarkdown file. Check the source for the corresponding SQL code. 
As you can see, there is no username or password hardcoded into the file. We use *environment variables* for passing in this information.
The calculated indices are the mean of **hourly** minimum, maximum, mean and 90% percentile temperature, aggregated live on query. 
Remember, that the database stores 5-min data. We do also exclude the first few days and the last day of the campaign and limit the used temperatures to a 
recorded light intensity range of 250 < light < 2500.

An overview over all used locations and their spatial distribution is given below:
```{r}
knitr::opts_chunk$set(echo = TRUE)
hobos.2019 %>%
  ggplot(aes(x=longitude, y=latitude)) +
  geom_point(aes(colour=radiation_influence, , size=mean_t)) +
  scale_size_continuous(range=c(3, 7))
```

Let's group by radiation_influence and have a look at the mean temperatures:

```{r}
hobos.2019 %>%
  ggplot(aes(x=radiation_influence, y=mean_t)) +
  geom_violin()
```

## analysis

Before you continue with in-depth analysis, or run a violin/boxplot on each index value, let's look at the correlations between the indices:
```{r}
correlation(hobos.2019)
```





```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
dbDisconnect(con)
```

